A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$ methods

### 2025-03-10 paper_v02/article.tex
first draft

% rho DCCA applications

@@

% DMCx2 applications

@@

The algorithm was tested with data and results from the \cite{RIBEIRO2025107419} paper. Details regarding data preparations can be found in the aforementioned paper. A comprehensive dataset of EEG (electroencephalogram) data, with 108 subjects, executing 12 experiments each, with the $\rho_{DCCA}$ and $DMC_{x}^{2}$ calculated for all experiments, using signals from four electrodes with 15742 points. The results were compared with the original ones, and the algorithms where validated.

>>>>

\color{red}Inserir parágrafo com citações de artigos que aplicam o $\rho_{DCCA}$\color{black}

@@

The method has been applied to study meteorological data~\citep{Brito2019}, have been tested statistically~\citep{filho2021-2}, used with the implementation of sliding windows~\citep{guedes2021-2}, to measure the contagion effect on stock market indexes~\citep{guedes2022d}, to produce statistical analysis between stock market behavior~\citep{zebende2022s} or analyze electroencephalogram (EEG) signals \citep{RIBEIRO2025107419}.

@@

The algorithm was tested with data and results from the \cite{RIBEIRO2025107419} paper. Details regarding data preparations can be found in the aforementioned paper. A comprehensive dataset of EEG, data, with 108 subjects, executing 12 experiments each, with the $\rho_{DCCA}$ and $DMC_{x}^{2}$ calculated for all experiments, using signals from four electrodes with 15742 points. The results were compared with the original ones, and the algorithms where validated.
